---
title: "The ggdiag package: a grammar for diagnostic graphics"
author: "Curso-r"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The ggdiag package is a attempt to unify the diagnostic analysis in R. For most models, diagnostic graphics are hard to customize or to obtain. In some cases, the expression for the residuals needed are not even implemented.

Our main goal is to create a simple grammar to plot diagnostic graphics that can be used for any kind of statistical model. The strategy is based in to main functions: the `diag_data()` function and the `plot.model_class()` functions.

The `diag_data()` function receive a fitted model and returns a `tibble` with several diagnostic measures, such as residuals, cook's distance, leverage etc, depending on the class of the model. It uses `broom::augment()` function to create most of the measures.

The `plot.model_class()` functions are S3 methods for the generic function `plot()`. They receive a object of class `diag_data` and return a specified diagnostic graphic. The graphics are made using the `ggplot2` package, and one can combine them with the 
`plotly::ggplolty()` function to identify points.

So far, only the `lm` and `glm` classes are available.

## Installing

```{r}
# How to install
devtools::load_all(".")
```


## Diagnostic for linear models

The examples below show how build diagnostic graphics is easy using the `diag_data()` and `plot()` functions. After fitting the linear model, the major job is to choose the graphic type. For `lm` class, the options currently available are: `"residuals"` (default), `"leverage"` and `"cook"`.

```{r}
library(ggilberto)

fit_lm <- lm(mpg ~ qsec, data = mtcars)
diag_lm <- diag_data(fit_lm)
```


```{r}
plot(diag_lm)
```


```{r}
plot(diag_lm, graphic = "leverage")
```


```{r}
plot(diag_lm, graphic = "cook")
```



## Diagnostic for generalized linear models

The main difference for the generalized linear models is the `"link"` option to the graphic argument. It produces a link function plot for assessing whether the link function is adequate.

```{r}
 fit_glm <- glm(mpg ~ qsec, family = Gamma(link = "log"), data = mtcars)
 diag_glm <- diag_data(fit_glm)
 
 plot(diag_glm, graphic = "link")
```
